\cvsection{Experience}
\begin{cventries}
  \cventry
    {Senior Software Engineer}
    {Major League Baseball}
    {Boulder, Colorado}
    {October 2017 - Present}
    {
      \begin{cvitems}
      \begin{footnotesize}
        \item {Read confidential specifications documents and worked directly with Apple engineers to organize and deploy a cross platform development effort in bringing our MLB apps into Apple's Universal Search (Apple TV app).}
        \item {Used advanced debugging techniques like analyzing stack traces, viewing object graphs, UI snapshots, and setting symbolic breakpoints/watchpoints with associated scripting.}
        \item {Worked on multi-platform development, creating a modernized internal SDK in Swift and rewriting legacy code. Managed framework dependencies and CI using Swift Package Manager, Carthage, and git sub modules.}
        \item {Authored code on a variety of Apple platforms including: iOS (Universal for iPhone and iPad), tvOS, watchOS, and CarPlay.}
        \end{footnotesize} 
      \end{cvitems}
    }
  \cventry
    {iOS Developer}
    {Starz Inc.}
    {Englewood, Colorado}
    {June 2017 - October 2017}
    {
      \begin{cvitems}
      \begin{footnotesize}
        \item {Performed full suite of code analysis using Instruments to find Memory Leaks, Bottlenecks, Energy Inefficiencies, and Zombies.}
        \item {Debugged REST based web service traffic by inspecting JSON requests and responses using proxy software Charles and made test requests using Postman.}
        \item {Worked in an agile environment on a team of 12 where all code was peer reviewed and then checked in via pull request. Collaborated in person on a daily basis, as well as using Skype/Slack/Screen Hero for collaboration with remote developers.}
        \item {Collaborated with QA and UI/UX team using Zeplin and confluence to ensure both functional and visual requirements were accurately adhered to.}
        \item {Worked on the entire suite of Starz Apple products and their shared SDK. This included a variety of platforms like tvOS, iOS (Universal for iPad and iPhone), as well as integration with Chromecast, Google Home, etc.}
        \end{footnotesize} 
      \end{cvitems}
    }
  \cventry
    {iOS Team Lead}
    {10-4 Systems}
    {Boulder, Colorado}
    {April 2016 - June 2017}
    {
      \begin{cvitems}
      \begin{footnotesize}
        \item {Was responsible for maintaining the entire deployment pipeline from code signing and provsioning, distribution certificates, and App Store Connect management.}
        \item {Setup stack of Fabric services to provide user authentication (Digits), credit card transactions (Stripe), stability information (Crashlytics), streamlined quality assurance (Beta) and deep link/referral marketing (Branch).}
        \item {Used development tools like Xcode server to set up continuous integration schedule and build analysis as well as JIRA to organize feature sets and file bug reports.}
        \item {Setup Unit Testing and UI Testing as part of the Continuous Integration environment. Code was written using Test Driven Development practices with XCTest classes along with accessibility inspector and UI recording to create robust UI tests.}
        \item {Extensive experience gained setting up APNS certificates and integrating them into a web server, as well as debugging common problems with pushes, customizing push presentation, and ingesting custom data from push bodies.}
        \end{footnotesize} 
      \end{cvitems}
    }
\end{cventries}
